\documentclass[a4paper,11pt]{article}

% Import packages
\usepackage[a4paper]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{proof}

% Change enumerate environments you use letters
\renewcommand{\theenumi}{\alph{enumi}}

% Set title, author name and date
\title{Informal proofs}
\author{Author: Kristoffer Højelse} % Do not include your name, as Peergrading is anonymous 
\date{\today}

\begin{document} 

\maketitle

\section{Notes}

\subsection{Proof the sum of two even numbers is even.}

Let $n, m \in \mathbb{Z}$ , such that  $n$ is even and $m$ is even.

By definition there exists $k, l \in \mathbb{Z}$ such that $n= 2 \cdot k$ and $m = 2 \cdot l$.

Therefore, $n+m = 2 \cdot k + 2 \cdot l$

$n+m = 2(k + l)$

Hence, by definition $n+m$ is even.

\subsection{Proof the sum of two Rational numbers is even.}

Let $r, q \in \mathbb{R}$ , such that  $r$ and $q$ is rational.

By definition there are $a,b,c,d, \in \mathbb{Z}$ such that $b \neq 0, d \neq 0$ and $r = \frac{a}{b}, q = \frac{c}{d}$.

Then, $r+q = \frac{a}{b} + \frac{c}{d} = \frac{ad + cb}{bd}$

Hence, $r+q$ is rational.

\subsection{Proof if the square of an integer is even, then the integer itself is even.}
if $n$ is not even, then $n$ is odd.

$ \neg Even(n) \to Odd(n) \equiv Even(n) \lor Odd(n) $


Let $n, \in Z$ , such that $n$ is not even.

By the Parity Theorem, $n$ is odd.  

By definition there exists $k \in Z$ such that $n = 2k+n$.

$n^2 = (2k+n)^2 = (4k)^2 + 2 \cdot 2k \cdot n + n^2$

$ 2 \cdot 2k^2 + 2 \cdot 2k + n $

$ 2(2k^2 + 2k) + n $

By definition $x^2$ is odd.

Hence, by the Parity Theorem, $n^2$ is not even.

\subsection{}

Propostion:

The negative of any irrational number is rational


For all real numbers $r$, if $r$ is irrational then $\neg r$ is irrational,

or

$$\forall r \in \mathbb{R}. r \notin \mathbb{Q} \to \neg r \notin \mathbb{Q}$$

Contraposition

$$\forall r \in \mathbb{R}. \neg (\neg r \notin \mathbb{Q}) \to \neg (r \notin Q) $$


$$\equiv \forall r \in \mathbb{R}. \neg r \in \mathbb{Q} \to r \in \mathbb{Q} $$

Let $r \in \mathbb{R}$ such that $- r \in \mathbb{Q}$

By def. there are $a,b \in \mathbb{Z}$ such that $b \neq 0$ and $- r = \frac{a}{b}$

$$(-r)(- 1) = \frac{a}{b} (- 1)$$

$$r = \frac{\neg a}{b}$$

Hence by def. $r$ is rational.

\subsection{Proof by contradiction}

Proposition:

There is no greatest integer.

$N \geq n$ 


$ \neg \exists N \in \mathbb{Z}. \forall n \in \mathbb{N}. N \geq n $

Assume $\exists N \in \mathbb{Z}. \forall n \in \mathbb{N}. N \geq n$

Let $N \in \mathbb{Z}$ such that $\forall n \in \mathbb{Z}. N \geq n$

substitute $n$ with $N+1$

In particular, this means $N \geq N + 1$

Contradiction. Therefore $\neg \exists N \in \mathbb{Z}. \forall n \in \mathbb{Z}. N \geq n$

\subsection{Proof by cases}

Propostion

For any integer $n$, $n^2 - n + 3$ is odd.


Let $n \in \mathbb{Z}$, By the Parity Theorem,

$n$ is even or $n$ is odd. We proceed by cases

1. $n$ is even


By def. there is some $k \in \mathbb{Z}$ such that $n = 2k$.


Hence,


$n^2 - n + 3 = (2k)^2 - 2k + 3$


udled


$= 2 \cdot (2k^2 - k + 1) + 1$

Hence, $n^2 - n + 3$ odd.

2. $n$ is odd

$\exists k$ such that $n = 2k + 1$

$n^2 - n + 3 = 2 \cdot 2k^2 + 2 \cdot 2k + 1 - (2k + 1)$

$= 2 (2k^2 + 2k + 1 - k) + 1$

\subsection{Proof by exhaustion}

\subsection{Disproving a Universal Statement}

Disproving Universal $\to$ find counterexample

\subsection{Disproving a Existential Statement}

Disproving Existential $\to$ proof all

\end{document}
